Considering scale in multilayer animal social networks

### 2020-06-14 paper/manuscript.Rmd
small edits lc results

In general, individuals in multilayer networks became more connected as the
spatial distance threshold defining caribou social associations increased. Mean
graph strength differed across habitat layers with similar and higher graph
strength in open and forage layers, and lower strength in forest layers (Figure
\@ref(fig:socres)). Individual graph strength increased sharply between 5 m and
100 m across habitat classes followed by decrease in rate after 100 m. These
results suggest the optimal social scale at which groups should be assigned is
likely somewhere between ~20 - 100 m based on the rate at which network metrics
stabilized. For ungulates, groups are often assigned based on 50 m threshold
(Lingle 2003; Lesmeries et al. 2018; Peignier et al. 2019), suggesting that
given similar quantities of data, ~50 m is likely an appropriate social scale
for generating social networks in caribou and similar species.

>>>>

Individuals in multilayer networks became more connected as the
spatial distance threshold increased. Mean
graph strength differed across habitat layers with similar and higher graph
strength in open and forage layers, and lower strength in forest layers (Figure
\@ref(fig:socres)). Individual graph strength increased sharply between 5 m and
100 m in all three habitat classes followed by a decrease in rate after 100 m. These
results suggest the optimal social scale at which groups should be assigned is
likely somewhere between ~20 - 100 m based on the rate at which network metrics
stabilized. For ungulates, groups are often assigned based on 50 m threshold
(Lingle 2003; Lesmeries et al. 2018; Peignier et al. 2019), suggesting that
given similar quantities of data, ~50 m is likely an appropriate social scale
for generating social networks in caribou and similar species.
